The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-02 manuscript.Rmd
Finsihing touches

>>>>

Parallel efforts to enable R for different cloud providers leads to some level of code fragmentation. This fact and to avoid lock-in motivated the [OpenFaaS project](https://www.openfaas.com/), that facilitates the deployment of functions and microservices to Kubernetes or Docker Swarm. OpenFaaS is language agnostic, it provides auto-scaling, metrics, and an API gateway.
Reduced boilerplate code is achieved via templates. R templates\footnote{OpenFaaS R templates: \href{https://github.com/analythium/openfaas-rstats-templates}{https://github.com/analythium/openfaas-rstats-templates}}
are provided based on Rocker's Debian and R-hub's [r-minimal](https://github.com/r-hub/r-minimal) Alpine images.
The templates use [multi-stage Docker builds](https://docs.docker.com/develop/develop-images/multistage-build/) to combine R base images with the OpenFaaS 'watchdog', a tiny Golang webserver that marshals an HTTP request and invokes the application. 
The R session uses \CRANpkg{plumber} or similar packages for the API endpoint with packages and data preloaded, thus minimizing response times.
